Linear response theory for core set identification

### 2012-06-12 writedown/linear.response/langevin.tex
fix bug, more considerations

    \begin{array}{ll}

@@

  &\,+

@@

  \nabla_q\mh(\vect q_s,\vect p_s)\cdot \vect D(\vect q_s,\vect p_s)\,

@@

  \Delta F_e(s) \vect D(\vect q_s,\vect p_s)\cdot \dd \vect p_s

@@

The first line of the r.h.s. of Eqn.~\eqref{eqn:girsanov-langevin-2}
is the time integrated excess entropy flux, which is
time-antisymmetric, while the second line is the excess dynamic
activity that is time-symmetric.  Inserting
Eqn.~\eqref{eqn:girsanov-langevin-2} into \eqref{eqn:noneq-pert-1}, we
have

@@

@@

  \vect p_s\cdot\vect D(\vect X_s)\,Q(\vect X_t)

@@

  \nabla_{\vect q}\mh(\vect X_s)\cdot\vect D(\vect X_s)\,Q(\vect X_t)

@@

  \vect D(\vect X_s)\,Q(\vect X_t)

@@

@@

  \vect p_s\cdot\vect D(\vect X_s)\,Q(\vect X_t)

@@

  \nabla_{\vect q}\mh(\vect X_s)

@@

  \,Q(\vect X_t)

@@

\subsection{Remarks and possibilities}
\bluec{
\begin{itemize}
\item It can be shown that 
  Eqn.~\eqref{eqn:noneq-pert-3} simply reduces to
  \eqref{eqn:eqi-pert-1}
  in the equilibrium case~\cite{baiesi2010nonequilibrium2}.
\item  Eqn.~\eqref{eqn:noneq-pert-3} shows that the trajectory average of
  $F_e^2$ is calculated from the trajectory average of $F_e^1$. We
  assume: (1) they start from the same initial distribution $\mu$, and
  (2) $F_e^2$ is not very far from $F_e^1$ so that the linear
  approximation is reasonably valid.  The condition (1) can be made
  weaker, for example $F_e^2$ starts from $\mu_2$ and $F_e^1$ starts
  from $\mu_1$, however, $\mu_2$ should be similar to $\mu_1$,
  otherwise the sampling is of poor accuracy.
\item Eqn.~\eqref{eqn:noneq-pert-3}, may be used in this way:
  assume we want to study the dynamics of $F_e^2$, which is very slow
  and difficult to handle directly.
  We can instead study the dynamics of $F_e^1$, which is
  similar to $F_e^2$, but is much faster, so that it can be handle by MD.
  And then use \eqref{eqn:noneq-pert-3} to calculate the averages of
  the target dynamics $F_e^2$.
  A possible choice of  $F_e^1$ may be  $F_e^1 = \alpha F_e^2,\ \alpha > 1$.
\item The perturbation $F_e^1$ can be kept a constant so that the
  system reaches a stationary state.
  $F_e^2$ is perturbation from that stationary state.
  The averages in
  \eqref{eqn:noneq-pert-3} can be calculated easier, because
  what we sample is the stationary state, rather the trajectories.
  When the system is far from the stationary state, the
  accuracy is low.
\item It may also be possible to study multiple reference dynamics,
  and use interpolations to increase the accuracy of the linear
  approximation.
\end{itemize}
}

>>>>

    \begin{array}{cc}

@@

  &\,-

@@

  \vect F^1(\vect q_s,\vect p_s)\cdot \vect D(\vect q_s,\vect p_s)\,

@@

  \Delta F_e(s) \vect D(\vect q_s,\vect p_s)\cdot \dd \vect p_s,

@@

where $\vect F^1(\vect q_s,\vect p_s) = -\nabla_{\vect q}\mh(\vect
q_s,\vect p_s) + F_e^1(t) \vect D(\vect q_s,\vect p_s)$.  The first
line of the r.h.s. of Eqn.~\eqref{eqn:girsanov-langevin-2} is the time
integrated excess entropy flux, which is time-antisymmetric, while the
second line is the excess dynamic activity that is time-symmetric.
Inserting Eqn.~\eqref{eqn:girsanov-langevin-2} into
\eqref{eqn:noneq-pert-1}, we have

@@

  \langle O(t)\rangle_{\mu}^{2}  -\langle O(t)\rangle_{\mu}^{1}

@@

  \vect p_s\cdot\vect D(\vect X_s)\,O(\vect X_t)

@@

  \vect F^1(\vect X_s)\cdot\vect D(\vect X_s)\,O(\vect X_t)

@@

  \vect D(\vect X_s)\,O(\vect X_t)

@@

  -\frac\beta 2

@@

  \vect p_s\cdot\nabla_{\vect q} V(\vect X_s)\,O(\vect X_t)

@@

  \vect F^1(\vect X_s)

@@

  \,O(\vect X_t)

@@

\subsection{Remarks and possibilities}
\bluec{
\begin{itemize}
\item It can be shown that 
  Eqn.~\eqref{eqn:noneq-pert-3} simply reduces to
  \eqref{eqn:eqi-pert-1}
  in the equilibrium case~\cite{baiesi2010nonequilibrium2}.
\item  Eqn.~\eqref{eqn:noneq-pert-3} shows that the trajectory average of
  $F_e^2$ is calculated from the trajectory average of $F_e^1$. We
  assume: (1) they start from the same initial distribution $\mu$, and
  (2) $F_e^2$ is not very far from $F_e^1$ so that the linear
  approximation is reasonably valid.  The condition (1) can be made
  weaker, for example $F_e^2$ starts from $\mu_2$ and $F_e^1$ starts
  from $\mu_1$, however, $\mu_2$ should be similar to $\mu_1$,
  otherwise the sampling is of poor accuracy.
  (2) means all possible trajectories of perturbation $F_e^2$ should be
  effciently sampled by perturbation $F_e^1$.
\item Eqn.~\eqref{eqn:noneq-pert-3}, may be used in this way:
  assume we want to study the dynamics of $F_e^2$, which is very slow
  and difficult to handle directly.
  We can instead study the dynamics of $F_e^1$, which is
  similar to $F_e^2$, but is much faster, so that it can be handle by MD.
  And then use \eqref{eqn:noneq-pert-3} to calculate the averages of
  the target dynamics $F_e^2$.
  A possible choice of  $F_e^1$ may be  $F_e^1 = \alpha F_e^2,\ \alpha > 1$.
  On the other hand, perturbation $F_e^2$ should be not very far
  from $F_e^1$, that means $F_e^2$ can not arbitrarily accelerate
  $F_e^1$. Fortunately we have the freedom to design $F_e^2$, therefore,
  an error estimate may help, and a path optimization of $F_e^2$
  may be developed.
\item The perturbation $F_e^1$ can be kept a constant so that the
  system reaches a stationary state.
  $F_e^2$ is perturbation from that stationary state.
  The averages in
  \eqref{eqn:noneq-pert-3} can be calculated easier, because
  what we sample is the stationary state, rather the trajectories.
  When the system is far from the stationary state, the
  accuracy is low. 
\item It may also be possible to study multiple reference dynamics,
  and use interpolations to increase the accuracy of the linear
  approximation.
\item Extension to nonlinear response?
\end{itemize}
}
